*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-26 Code/Manuscript_O2.Rmd
added page breaks
Fixed caption not being knitted to WORD for protein figures

XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
```{r MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MED4ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade).**",

                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
                    "Numbers over each bar are fmole target protein per ug total protein.",

knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAnnotated.png"))
```

@@

XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
```{r MIT9313ProteinAnnotated, fig.cap = MIT9313ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MIT9313ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade).  **",
                                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
                    "Numbers over each bar are fmole target protein per ug total protein.",

knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAnnotated.png"))
```

@@

## *Prochlorococcus* genomic capacities for electron dissipation and DNA repair {.unnumbered}

>>>>

XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX

```{r  MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MED4ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade.  **",
                                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
                                    "Numbers over each bar are fmole target protein per ug total protein.",
                                    .sep = " ")

knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAnnotated.png"))

@@

XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX

```{r  MIT9313ProteinAnnotated, fig.cap = MIT9313ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MIT9313ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade).  **",
                                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
                                    "Numbers over each bar are fmole target protein per ug total protein.",
                                    .sep = " ")

knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAnnotated.png"))

@@
